### 2018-04-04 Sections/economics_of_the_quantum_internet.tex
Quantcoin

\begin{figure}[!htb]
\includegraphics[width=0.4\textwidth]{cost_of_comp_n} \\
\includegraphics[width=0.4\textwidth]{cost_of_comp_n2} \\
\includegraphics[width=0.4\textwidth]{cost_of_comp_2n}
\caption{Examples of the temporal dynamics of the cost of computation for different scaling functions and exponential growth rates. Units are \mbox{$C_0=N_0=n=1$}.\comment{Redo these}}\label{fig:econ_cost_of_comp}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.4\textwidth]{forward_cont_pricing_mod}
\caption{Forward contract price on a single physical qubit to be delivered at time $T$ in the future. Units are \mbox{$C_0=1$}.\comment{Redo fig, outdated}}\label{fig:forward_cont_pricing_mod}
\end{figure}

@@

>>>>

\begin{figure}[!htb]
\includegraphics[width=0.4\textwidth]{cost_of_comp_n} \\
\includegraphics[width=0.4\textwidth]{cost_of_comp_n2} \\
\includegraphics[width=0.4\textwidth]{cost_of_comp_2n}
\caption{Examples of the temporal dynamics of the cost of computation for different scaling functions and exponential growth rates. Units are \mbox{$C_0=N_0=n=1$}.}\label{fig:econ_cost_of_comp}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.4\textwidth]{forward_cont_pricing_mod_1}\\
\includegraphics[width=0.4\textwidth]{forward_cont_pricing_mod_2}
\caption{Forward price on a computation to be delivered at time $T$ in the future, in units \mbox{$C_0=N_0=1$}, where we are assuming an exponential scaling function, \mbox{$f_\text{sc}(n)=e^n$}.}\label{fig:forward_cont_pricing_mod}
\end{figure}

@@

%
% QuantCoin - A Computation-Backed Currency]
%

\subsection{QuantCoin\texttrademark -- A computation-backed currency}\index{Computation-backed currency}\index{QuantCoin\texttrademark}

The advent of cryptocurrencies\index{Cryptocurrency} (Sec.~\ref{sec:bitcoin_blockchain}) places the death of fiat currency\index{Fiat currency} on the horizon. Central banks around the world have been consistently inflating and devaluing national currencies, destroying their integrity through print-on-demand monetary policies.

What makes a sound currency\index{Sound currency}? First of all, it must exhibit scarcity\index{Scarcity} and be difficult or impossible to counterfeit\index{Counterfeit} -- it should not be possible to forge unlimited quantities out of thin air, a quality not inherent to fiat currency. Second, its abundance should exhibit relative stablility and predictability over time, so as to create a stable money supply\index{Money supply}. For these reasons, gold for thousands of years was accepted as legal tender, since it is naturally scarce and much work must be invested into its production. For the same reasons, emerging cryptocurrencies have become widely adopted and even the norm in hyper-inflating countries like Venezuela where fiat currency has lost all integrity, as they exhibit these same traits. But rather than scarcity of a natural resource, we are dealing with artificial scarcity of bit-strings, cryptographically enforced to satisfy certain mathematical properties that cannot be easily counterfeited.

We propose that units of quantum computation meet these criteria very well. The only way to forge new computations is via investment into infrastructure, which has direct monetary cost and cannot be mitigated. Recent history has shown us that Moore's Law\index{Moore's Law} has made the growth in classical computing power highly predictable and relatively stable over time, and it is to be expected that a quantum Moore's Law will hold.

Time-shares in unified computing power over the quantum network, via licensing out qubits from hardware owners, would provide all these essential desired qualities of a sound currency. It can be envisaged that forward contracts in compute-time (Sec.~\ref{sec:for_contr}) would acts as a good basis for backing a currency. Since these are simple paper contracts, they lend themselves to straightforward, low-overhead trading on international markets.

Were a computation-backed currency to emerge -- QuantCoin\texttrademark\index{QuantCoin\texttrademark} -- this would immediately further incentivise investment into expansion of quantum computational hardware, as it could be directly exchanged for currency. The implications for compute-intensive industries would be immense, as there would be negligible transaction costs associated with the purchase of computation -- since contracts in computation \textit{are} the accepted currency -- thereby driving forward the next technological revolution.

\textit{--- End the Fed.}
